Sexual selection improves population fitness: a meta-analysis

### 2018-11-26 meta_analysis_sexual_selection_pop_fitness.Rmd
Lots of changes to the data, supp and reviewer comments

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(car)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
library(rstan) #Note that installation requires some effort: dependency for brms
library(brms) 
library(backports) #seems to be a dependency
library(bayesplot)
#devtools::install_github("mvuorre/brmstools")
library(brmstools)
library(metaAidR) # install.packages("metaAidR")
library(cowplot)
source("I2_function.R") #Adapted function for obtaining I2 with CIs
source("Vdodge_function.R") # nice function for ggplot
source("Tidy_functions_for_brms.R") #Tidy functions for making model tables for brms
```

```{r echo=FALSE, results='hide', warning=FALSE}
library(knitr) # set up cacheing to save time when re-building the html document
```
`r opts_chunk$set(cache=TRUE)`

@@

### Forest Plot

```{r, fig.height=18, fig.width=12}
# Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
full_dataset$Outcome_f = factor(full_dataset$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

@@

  scale_x_continuous(limits=c(-3.35, 12), 
                     breaks = c(-3, -2, -1, 0, 1, 2, 3), 
                     name='                              Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +

@@

  theme(strip.text.y = element_text(angle = 0, size = 8, margin = margin(t=15, r=15, b=15, l=15)), 
        strip.background = element_rect(colour = NULL,
                                        linetype = "blank",
                                        fill = "gray90"),
        text = element_text(size=11),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=12), 
        legend.title=element_text(size=12, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0, size = 12))

@@

#### Run the Bayesian meta-analysis to get the overall effect
```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
if(!file.exists("data/grand.mean.bayes.rds")){
  grand.mean.bayes <- brm(g | se(SE)  ~ 1 # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                          + (1|Study.ID)
                          + (1|Outcome)
                          + (1|Taxon), 
                          family = "gaussian", 
                          seed = 1,
                          cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                          control = list(adapt_delta = 0.9999, max_treedepth = 15),
                          data = full_dataset %>% mutate(SE = sqrt(var.g)))

  saveRDS(grand.mean.bayes, "data/grand.mean.bayes.rds") # Save to avoid re-running during knit
}
grand.mean.bayes <- readRDS("data/grand.mean.bayes.rds")
```

These estimates are presented in the text of the Results section. The test statistic is either the p-value (REML) or Bayes factor comparing the effect size to zero (Bayesian).
```{r}
pander(data.frame(
  Method = c("REML", "Bayesian"),
  Grand_mean_effect_size_g = c(forest.model$b, summary(grand.mean.bayes)$fixed[,"Estimate"]),
  Lower_95_CI = c(forest.model$ci.lb, summary(grand.mean.bayes)$fixed[,"l-95% CI"]),
  Upper_95_CI = c(forest.model$ci.ub, summary(grand.mean.bayes)$fixed[,"u-95% CI"]),
  Test_statistic = c(forest.model$pval, hypothesis(grand.mean.bayes, "Intercept > 0")$hypothesis$Evid.Ratio)), digits = 2) 
```

@@

components.brms <- readRDS(file = "data/components.brms.rds")

make_text_summary(components.brms) %>% 
  add_significance_stars() %>% 
  tibble::rownames_to_column("Model Parameter") %>% 
  pander(split.cell = 40, split.table = Inf)
```

**Table S6** Summary of model predictions for 20 fitness components. In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot) using the Bayesian values. Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0. Where values greater than 1 correspond to higher likelihood of the effect size being positive and values less than 1 suggest that the effect size is more likely to be negative. The right side of the table provides the REML estimates with SE and CIs.

@@

#Name columns
colnames(brms.predictions) <- c("Fitness Component", "Bayes Prediction", "Bayes SE", "Bayes L_95_CI", "Bayes U_95_CI")

outcome.list.factor <-  c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')

@@

# Obtain Bayes Factor of likelihood that the outcome is greater than 0
BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
# Obtain BF for all components
Hypotheses <- list()
BFs <- list()
Hypotheses[["Behavioural Plasticity"]] <- hypothesis(components.brms, "Intercept > 0") #Intercept in model, need to do it by itself
BFs[["Behavioural Plasticity"]] <- Hypotheses[["Behavioural Plasticity"]][["hypothesis"]][["Evid.Ratio"]]
for (i in BF.outcome.list){
  Hypotheses[[i]] <- hypothesis(components.brms, paste("Intercept + Outcome", i," > 0", sep = ""))
  BFs[[i]] <- Hypotheses[[i]][["hypothesis"]][["Evid.Ratio"]]
} #Loop over all fitness compoinents

@@

@@

>>>>

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(car)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
library(rstan) #Note that installation requires some effort: dependency for brms
#devtools::install_github("paul-buerkner/brms")
library(brms) 
library(backports) #seems to be a dependency
library(bayesplot)
#devtools::install_github("mvuorre/brmstools")
library(brmstools)
library(metaAidR) # install.packages("metaAidR")
library(cowplot)
#devtools::install_github("eclarke/ggbeeswarm")
library(ggbeeswarm)
source("I2_function.R") #Adapted function for obtaining I2 with CIs
source("Vdodge_function.R") # nice function for ggplot
source("Tidy_functions_for_brms.R") #Tidy functions for making model tables for brms
```

```{r echo=FALSE, results='hide', warning=FALSE}
knitr::opts_knit$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
```
`r opts_chunk$set(cache=TRUE)`

@@

#### Run the Bayesian meta-analysis to get the overall effect
```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
if(!file.exists("data/grand.mean.bayes.rds")){
  grand.mean.bayes <- brm(g | se(SE)  ~ 1 # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                          + (1|Study.ID)
                          + (1|Outcome)
                          + (1|Taxon), 
                          family = "gaussian", 
                          seed = 1,
                          cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                          control = list(adapt_delta = 0.999, max_treedepth = 15),
                          data = full_dataset %>% mutate(SE = sqrt(var.g)))

  saveRDS(grand.mean.bayes, "data/grand.mean.bayes.rds") # Save to avoid re-running during knit
}
grand.mean.bayes <- readRDS("data/grand.mean.bayes.rds")

```

These estimates are presented in the text of the Results section. The test statistic is either the p-value (REML) or Bayes factor (BF) comparing the effect size to zero (Bayesian).
```{r}
pander(data.frame(
  Method = c("REML", "Bayesian"),
  Grand_mean_effect_size_g = c(forest.model$b, summary(grand.mean.bayes)$fixed[,"Estimate"]),
  Lower_95_CI = c(forest.model$ci.lb, summary(grand.mean.bayes)$fixed[,"l-95% CI"]),
  Upper_95_CI = c(forest.model$ci.ub, summary(grand.mean.bayes)$fixed[,"u-95% CI"]),
  Test_statistic = c(forest.model$pval, hypothesis(grand.mean.bayes, "Intercept > 0")$hypothesis$Evid.Ratio)), digits = 2) 
```

### Effect of sexual selection on direct, indirect and ambiguous measures of fitness

The mean effect size may also be calculated for each of the three fitness trait classes (Ambiguous, Indirect and Direct)

```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
if(!file.exists("data/grand.mean.class.bayes.rds")){
  grand.mean.class.bayes <- brm(g | se(SE)  ~ Outcome.Class # Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                          + (1|Study.ID)
                          + (1|Taxon), 
                          family = "gaussian", 
                          seed = 1,
                          cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                          control = list(adapt_delta = 0.9999, max_treedepth = 15),
                          data = full_dataset %>% mutate(SE = sqrt(var.g)))

  saveRDS(grand.mean.class.bayes, "data/grand.mean.class.bayes.rds") # Save to avoid re-running during knit
}
grand.mean.class.bayes <- readRDS("data/grand.mean.class.bayes.rds")

# Define new data for prediction
brms.newdata.class <- as.data.frame(expand.grid(Outcome.Class = unique(full_dataset$Outcome.Class)))

# Get average SE: useful if using predict, but not fitted
av.se.g.class <- full_dataset %>% group_by(Outcome.Class) %>% summarise(mean = mean(sqrt(var.g)))
brms.newdata.class$SE <- av.se.g.class$mean

# Find the fitted values (i.e. predictions from the linear mixed model fit by brms)
brms.predict.class <- fitted(grand.mean.class.bayes, newdata = brms.newdata.class, re_formula = NA) %>% as.data.frame()
brms.predictions.class <- data.frame(brms.newdata.class$Outcome.Class, brms.predict.class$Estimate, brms.predict.class$Est.Error, brms.predict.class$Q2.5, brms.predict.class$Q97.5)

#Name columns
colnames(brms.predictions.class) <- c("Relationship to Fitness", "Bayes Prediction", "Bayes SE", "Bayes LCI", "Bayes UCI")

outcome.list.factor.class <-  c('Indirect', 'Ambiguous', 'Direct')

brms.predictions.class <- brms.predictions.class[match(outcome.list.factor.class, brms.predictions.class$`Relationship to Fitness`),]
rownames(brms.predictions.class) <- NULL
sample.sizes.outcome.class <- as.data.frame(table(full_dataset$Outcome.Class))
colnames(sample.sizes.outcome.class) <- c("Relationship to Fitness", "n")
fitness.class.predictions <- left_join(brms.predictions.class, sample.sizes.outcome.class, by = "Relationship to Fitness")

# Obtain Bayes Factor of likelihood that the outcome is greater than 0
BF.outcome.class.list <-  c('Ambiguous', 'Direct')
# Obtain BF for all components
Hypotheses <- list()
BFs <- list()
Hypotheses[["Indirect"]] <- hypothesis(grand.mean.class.bayes, "Intercept > 0") #Intercept in model, need to do it by itself
BFs[["Indirect"]] <- Hypotheses[["Indirect"]][["hypothesis"]][["Evid.Ratio"]]
for (i in BF.outcome.class.list){
  Hypotheses[[i]] <- hypothesis(grand.mean.class.bayes, paste("Intercept + Outcome.Class", i," > 0", sep = ""))
  BFs[[i]] <- Hypotheses[[i]][["hypothesis"]][["Evid.Ratio"]]
} #Loop over all fitness compoinents

# Now for REML. Not easy because the predict function for rma.mv has an odd interface
model.fitness.class.REML <- rma.mv(g, var.g, mods = ~ 1 + Outcome.Class,
                         random = list(~ 1 | Study.ID,
                                       ~ 1 | Taxon),
                         method = "REML",
                         data = full_dataset)

get.predictions.class <- function(newdata){
  Indirect <- 0; Ambiguous <- 0; Direct <- 0
  if(newdata[1] == 'Ambiguous') Ambiguous<-1
  if(newdata[1] == 'Direct') Direct<-1

  predict(model.fitness.class.REML, newmods=c(Ambiguous, Direct))
}
# Get the predictions for each combination of moderators
predictions.class <- as.data.frame(expand.grid(Outcome.Class = outcome.list.factor.class))
predictions.class <- cbind(predictions.class, do.call("rbind", apply(predictions.class, 1, get.predictions.class))) %>%
  select(Outcome.Class, pred, se, ci.lb, ci.ub) 
for(i in 2:5) predictions.class[,i] <- unlist(predictions.class[,i])

colnames(predictions.class) <- c("Relationship to Fitness", "REML Prediction", "REML SE", "REML LCI", "REML UCI")
predictions.class <- format(predictions.class, digits = 2)

fitness.class.predictions <- fitness.class.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% `row.names<-`(NULL) %>% format(digits = 2)

left_join(fitness.class.predictions, predictions.class, by = "Relationship to Fitness") %>% pander(split.table = Inf, digits = 2)

```

From this data we can generate a forest plot with the following:

```{r}
pd <- position_dodge(0.3)
predictions.class[,2:5] <- sapply(predictions.class[,2:5], as.numeric)
forest.plot.class <- predictions.class %>%
  rename(Outcome.Class = "Relationship to Fitness",
         Pred = 'REML Prediction',
         LCI = 'REML LCI',
         UCI = 'REML UCI') %>%
  mutate(Outcome.Class = factor(Outcome.Class, levels = c("Direct", "Indirect", "Ambiguous"))) %>%
  ggplot(aes(x = Outcome.Class, y = Pred, colour = Outcome.Class, fill = Outcome.Class)) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0.23, linetype = 2, colour = "steelblue", size = 1) +
  geom_quasirandom(data = full_dataset %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female"),
         Outcome.Class = factor(Outcome.Class, levels = c("Direct", "Indirect", "Ambiguous"))),
                   aes(x = Outcome.Class, y = g), alpha=0.4) +
  geom_errorbar(mapping = aes(ymin = LCI, ymax = UCI), width = 0, position = pd, size=1, colour = "grey10") + 
  geom_point(position = pd, size=3.25, shape = 23, stroke = .75, color = "grey10") + 
  ylab("Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]") +
  theme_minimal(12) +
  theme(panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(), legend.position = "none") +
  scale_color_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
                     name = "Relationship\nto fitness")+
  scale_fill_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
                     name = "Relationship\nto fitness")+
  xlab("Relationship to Fitness")+
  coord_flip()

forest.plot.class
```

#### Forest Plot

```{r, fig.height=18, fig.width=12}
# Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
full_dataset$Outcome_f = factor(full_dataset$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

@@

  scale_x_continuous(limits=c(-3.35, 4.25), 
                     breaks = c(-3, -2, -1, 0, 1, 2, 3), 
                     name='Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +

@@

  theme(strip.text.y = element_text(angle = 0, size = 8, margin = margin(t=15, r=15, b=15, l=15)), 
        strip.background = element_rect(colour = NULL,
                                        linetype = "blank",
                                        fill = "gray90"),
        text = element_text(size=11),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=12), 
        legend.title=element_text(size=12, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 14))

@@

@@

components.brms <- readRDS(file = "data/components.brms.rds") 
```

**Table S6** Summary of model predictions for 20 fitness components. In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot) using the Bayesian values. Additionally, Bayes Factors (BF) are presented as the likelihood ratio that the effect size is greater than 0. Where values greater than 1 correspond to higher likelihood of the effect size being positive and values less than 1 suggest that the effect size is more likely to be negative. The right side of the table provides the REML estimates with SE and 95 % CIs.

@@

#Name columns
colnames(brms.predictions) <- c("Fitness Component", "Bayes Prediction", "Bayes SE", "Bayes LCI", "Bayes UCI")

outcome.list.factor <-  c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')

@@

# Obtain Bayes Factor of likelihood that the outcome is greater than 0
BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
# Obtain BF for all components
Hypotheses <- list()
BFs <- list()
Hypotheses[["Behavioural Plasticity"]] <- hypothesis(components.brms, "Intercept > 0") #Intercept in model, need to do it by itself
BFs[["Behavioural Plasticity"]] <- Hypotheses[["Behavioural Plasticity"]][["hypothesis"]][["Evid.Ratio"]]
for (i in BF.outcome.list){
  Hypotheses[[i]] <- hypothesis(components.brms, paste("Intercept + Outcome", i," > 0", sep = ""))
  BFs[[i]] <- Hypotheses[[i]][["hypothesis"]][["Evid.Ratio"]]
} #Loop over all fitness compoinents

@@

Individual Meta-analyses for each fitness related trait with n>3:

```{r, warning = FALSE}
outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Male Attractiveness', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
                          mods = ~ 1, 
                          method = "REML",
                          random = list(~ 1 | Study.ID,
                                       ~ 1 | Taxon),
                          subset = (Outcome_f == x),
                          data = full_dataset))

df.list <- as.data.frame(do.call("rbind", outcome.models)) # data frame of model results

simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))
# simple.frame$vi <- as.matrix(simple.frame$vi)
# simple.frame$W <- diag(1/(simple.frame$vi))
# 
# XO <- model.matrix(model.complete2)
# PO <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
# 100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))

#I couldn't get mapply to work when calculating I2 so I calculated them manually.

#Body Size 
restricted.dataBS <- full_dataset %>% filter(full_dataset$Outcome == "Body Size")

#Run estimate of heterogeneity
WBS = diag(1/restricted.dataBS$var.g)
XBS = model.matrix(outcome.models[["Body Size"]])
PBS = WBS - WBS %*% XBS %*% solve(t(XBS) %*% WBS %*% XBS) %*% t(XBS) %*% WBS
BodySizeI2 <- 100 * sum(outcome.models[["Body Size"]]$sigma2) / (sum(outcome.models[["Body Size"]]$sigma2) + (outcome.models[["Body Size"]]$k-outcome.models[["Body Size"]]$p)/sum(diag(PBS)))

#Development Rate 
restricted.dataDR <- full_dataset %>% filter(full_dataset$Outcome == "Development Rate")

#Run estimate of heterogeneity
W = diag(1/restricted.dataDR$var.g)
X = model.matrix(outcome.models[["Development Rate"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
DevelopmentRateI2 <- 100 * sum(outcome.models[["Development Rate"]]$sigma2) / (sum(outcome.models[["Development Rate"]]$sigma2) + (outcome.models[["Development Rate"]]$k-outcome.models[["Development Rate"]]$p)/sum(diag(P)))

#Early Fecundity 
restricted.dataEF <- full_dataset %>% filter(full_dataset$Outcome == "Early Fecundity")

#Run estimate of heterogeneity
W = diag(1/restricted.dataEF$var.g)
X = model.matrix(outcome.models[["Early Fecundity"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
EarlyFecundityI2 <- 100 * sum(outcome.models[["Early Fecundity"]]$sigma2) / (sum(outcome.models[["Early Fecundity"]]$sigma2) + (outcome.models[["Early Fecundity"]]$k-outcome.models[["Early Fecundity"]]$p)/sum(diag(P)))

#Immunity
restricted.dataI <- full_dataset %>% filter(full_dataset$Outcome == "Immunity")

#Run estimate of heterogeneity
W = diag(1/restricted.dataI$var.g)
X = model.matrix(outcome.models[["Immunity"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ImmunityI2 <- 100 * sum(outcome.models[["Immunity"]]$sigma2) / (sum(outcome.models[["Immunity"]]$sigma2) + (outcome.models[["Immunity"]]$k-outcome.models[["Immunity"]]$p)/sum(diag(P)))

#Mating Duration
restricted.dataMD <- full_dataset %>% filter(full_dataset$Outcome == "Mating Duration")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMD$var.g)
X = model.matrix(outcome.models[["Mating Duration"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingDurationI2 <- 100 * sum(outcome.models[["Mating Duration"]]$sigma2) / (sum(outcome.models[["Mating Duration"]]$sigma2) + (outcome.models[["Mating Duration"]]$k-outcome.models[["Mating Duration"]]$p)/sum(diag(P)))

#Mutant Frequency
restricted.dataMF <- full_dataset %>% filter(full_dataset$Outcome == "Mutant Frequency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMF$var.g)
X = model.matrix(outcome.models[["Mutant Frequency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MutantFrequencyI2 <- 100 * sum(outcome.models[["Mutant Frequency"]]$sigma2) / (sum(outcome.models[["Mutant Frequency"]]$sigma2) + (outcome.models[["Mutant Frequency"]]$k-outcome.models[["Mutant Frequency"]]$p)/sum(diag(P)))

#Fitness Senescence
restricted.dataFS <- full_dataset %>% filter(full_dataset$Outcome == "Fitness Senescence")

#Run estimate of heterogeneity
W = diag(1/restricted.dataFS$var.g)
X = model.matrix(outcome.models[["Fitness Senescence"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
FitnessSenescenceI2 <- 100 * sum(outcome.models[["Fitness Senescence"]]$sigma2) / (sum(outcome.models[["Fitness Senescence"]]$sigma2) + (outcome.models[["Fitness Senescence"]]$k-outcome.models[["Fitness Senescence"]]$p)/sum(diag(P)))

#Lifespan
restricted.dataL <- full_dataset %>% filter(full_dataset$Outcome == "Lifespan")

#Run estimate of heterogeneity
W = diag(1/restricted.dataL$var.g)
X = model.matrix(outcome.models[["Lifespan"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
LifespanI2 <- 100 * sum(outcome.models[["Lifespan"]]$sigma2) / (sum(outcome.models[["Lifespan"]]$sigma2) + (outcome.models[["Lifespan"]]$k-outcome.models[["Lifespan"]]$p)/sum(diag(P)))

#Male Attractiveness
restricted.dataMA <- full_dataset %>% filter(full_dataset$Outcome == "Male Attractiveness")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMA$var.g)
X = model.matrix(outcome.models[["Male Attractiveness"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MaleAttractivenessI2 <- 100 * sum(outcome.models[["Male Attractiveness"]]$sigma2) / (sum(outcome.models[["Male Attractiveness"]]$sigma2) + (outcome.models[["Male Attractiveness"]]$k-outcome.models[["Male Attractiveness"]]$p)/sum(diag(P)))

#Mating Frequency
restricted.dataMF <- full_dataset %>% filter(full_dataset$Outcome == "Mating Frequency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMF$var.g)
X = model.matrix(outcome.models[["Mating Frequency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingFrequencyI2 <- 100 * sum(outcome.models[["Mating Frequency"]]$sigma2) / (sum(outcome.models[["Mating Frequency"]]$sigma2) + (outcome.models[["Mating Frequency"]]$k-outcome.models[["Mating Frequency"]]$p)/sum(diag(P)))

#Mating Latency
restricted.dataML <- full_dataset %>% filter(full_dataset$Outcome == "Mating Latency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataML$var.g)
X = model.matrix(outcome.models[["Mating Latency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingLatencyI2 <- 100 * sum(outcome.models[["Mating Latency"]]$sigma2) / (sum(outcome.models[["Mating Latency"]]$sigma2) + (outcome.models[["Mating Latency"]]$k-outcome.models[["Mating Latency"]]$p)/sum(diag(P)))

#Mating Success
restricted.dataMS <- full_dataset %>% filter(full_dataset$Outcome == "Mating Success")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMS$var.g)
X = model.matrix(outcome.models[["Mating Success"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingSuccessI2 <- 100 * sum(outcome.models[["Mating Success"]]$sigma2) / (sum(outcome.models[["Mating Success"]]$sigma2) + (outcome.models[["Mating Success"]]$k-outcome.models[["Mating Success"]]$p)/sum(diag(P)))

#Ejaculate Quality and Production
restricted.dataEQ <- full_dataset %>% filter(full_dataset$Outcome == "Ejaculate Quality and Production")

#Run estimate of heterogeneity
W = diag(1/restricted.dataEQ$var.g)
X = model.matrix(outcome.models[["Ejaculate Quality and Production"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
EjaculateQualityI2 <- 100 * sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) / (sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) + (outcome.models[["Ejaculate Quality and Production"]]$k-outcome.models[["Ejaculate Quality and Production"]]$p)/sum(diag(P)))

#Extinction Rate
restricted.dataER <- full_dataset %>% filter(full_dataset$Outcome == "Extinction Rate")

#Run estimate of heterogeneity
W = diag(1/restricted.dataER$var.g)
X = model.matrix(outcome.models[["Extinction Rate"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ExtinctionRateI2 <- 100 * sum(outcome.models[["Extinction Rate"]]$sigma2) / (sum(outcome.models[["Extinction Rate"]]$sigma2) + (outcome.models[["Extinction Rate"]]$k-outcome.models[["Extinction Rate"]]$p)/sum(diag(P)))

#Offspring Viability
restricted.dataOV <- full_dataset %>% filter(full_dataset$Outcome == "Offspring Viability")

#Run estimate of heterogeneity
W = diag(1/restricted.dataOV$var.g)
X = model.matrix(outcome.models[["Offspring Viability"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
OffspringViabilityI2 <- 100 * sum(outcome.models[["Offspring Viability"]]$sigma2) / (sum(outcome.models[["Offspring Viability"]]$sigma2) + (outcome.models[["Offspring Viability"]]$k-outcome.models[["Offspring Viability"]]$p)/sum(diag(P)))

#Reproductive Success
restricted.dataRS <- full_dataset %>% filter(full_dataset$Outcome == "Reproductive Success")

#Run estimate of heterogeneity
W = diag(1/restricted.dataRS$var.g)
X = model.matrix(outcome.models[["Reproductive Success"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ReproductiveSuccessI2 <- 100 * sum(outcome.models[["Reproductive Success"]]$sigma2) / (sum(outcome.models[["Reproductive Success"]]$sigma2) + (outcome.models[["Reproductive Success"]]$k-outcome.models[["Reproductive Success"]]$p)/sum(diag(P)))

simple.frame$I2 <- c(NA, BodySizeI2, DevelopmentRateI2, EarlyFecundityI2, ImmunityI2, MaleAttractivenessI2, MatingDurationI2, NA, MutantFrequencyI2, FitnessSenescenceI2, LifespanI2, MatingFrequencyI2, MatingLatencyI2, MatingSuccessI2, NA, EjaculateQualityI2, ExtinctionRateI2, OffspringViabilityI2, ReproductiveSuccessI2)

outcome.frame <- format(simple.frame, digits = 2)
outcome.frame <- add_rownames(outcome.frame, "Outcome")
outcome.frame$b <- as.numeric(outcome.frame$b)
outcome.frame$k <- as.numeric(outcome.frame$k)
outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
outcome.frame$I2 <- as.numeric(outcome.frame$I2)
outcome.frame$Class <- c("Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Direct", "Direct", "Direct")

outcome.frame %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)

```

@@

##Meta-analysis using lnRR

As per reviewers comments, we can use the log-response ratio instead of hedges g. Here we use the ``metafor`` function escalc.

```{r}
lnRR.data <- 
escalc(measure = "ROM",
       m1i = mean.high, 
       m2i = mean.low,
       sd1i = sd.high,
       sd2i = sd.low,
       n1i = n.high,
       n2i = n.low,
       vtype = "LS",
       data = full_dataset, var.names=c("lnRR","lnRR_var"), digits=4) %>% 
  filter(lnRR != "NA") %>% 
  mutate(lnRR = round(lnRR, 3)*Positive.Fitness,
         Sex = relevel(Sex, ref = "M"),
         Environment = relevel(Environment, ref = "Unstressed"),
         Taxon = relevel(Taxon, ref = "Beetle"),
         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"))
